A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-16 results.tex
Finished the first draft

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/tonFigs/throughput-sat-SR-TON.eps}
		\caption{Average throughput for a saturated network with channel error ($p_e=0.1$). Curves called "aggr" reffer to values of $\gamma=1$, while "halv" refers to a schedule halving (see Section~\ref{aggr} and Algorithm~\ref{alg:schedRest}). \emph{dynStick} reffers to curvers where the node's stickiness is temporarily increased to two after a successful reduction of the schedule. \textcolor{red}{this figure needs new data files}}
		\label{fig:throughput-sat-SR}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/tonFigs/timeBetSxTx-sat-SR-TON.eps}
		\caption{Time between successful transmissions for a saturated network with channel error ($p_e=0.1$). Curves called "aggr" reffer to values of $\gamma=1$, while "halv" refers to a schedule halving (see Section~\ref{aggr} and Algorithm~\ref{alg:schedRest}). \emph{dynStick} reffers to curvers where the node's stickiness is temporarily increased to two after a successful reduction of the schedule. \textcolor{red}{this figure needs new data files}}
		\label{fig:timeBetSxTx-sat-SR}
	\end{figure}

>>>>

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/tonFigs/throughput-sat-SR-TON.eps}
		\caption{Average throughput for a saturated network with channel error ($p_e=0.1$). Curves called "aggr" reffer to values of $\gamma=1$, while "halv" refers to a schedule halving (see Section~\ref{aggr} and Algorithm~\ref{alg:schedRest}). \emph{dynStick} reffers to curvers where the node's stickiness is temporarily increased to two after a successful reduction of the schedule}
		\label{fig:throughput-sat-SR}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/tonFigs/timeBetSxTx-sat-SR-TON.eps}
		\caption{Time between successful transmissions for a saturated network with channel error ($p_e=0.1$). Curves called "aggr" reffer to values of $\gamma=1$, while "halv" refers to a schedule halving (see Section~\ref{aggr} and Algorithm~\ref{alg:schedRest}). \emph{dynStick} reffers to curvers where the node's stickiness is temporarily increased to two after a successful reduction of the schedule}
		\label{fig:timeBetSxTx-sat-SR}
	\end{figure}
